%-------------------------
% Updated Resume in LaTeX
% Author : Ashutosh Sharma
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% \usepackage{CormorantGaramond}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\setlength{\footskip}{4.08003pt}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% ----- Custom Commands -----
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{0pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-5pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% ----- Document -----
\begin{document}

\begin{center}
    \textbf{\Huge Ashutosh Sharma} \\ \vspace{1pt}
    {Oshawa, ON, Canada} $|$
    \small +1 647-226-0267 $|$ \href{mailto:asrma.sharma@gmail.com}{\underline{asrma.sharma@gmail.com}} $|$
    \href{https://linkedin.com/in/asrma7}{\underline{linkedin.com/in/asrma7}} $|$
    \href{https://ashutoshportfolio.site}{\underline{ashutoshportfolio.site}}
\end{center}

% ----- Summary -----
\section*{Professional Summary}
Full-Stack Developer experienced in building scalable applications and microservices using \textbf{Golang}, \textbf{Python}, and \textbf{TypeScript}. Skilled in designing APIs, database schemas, and automation workflows. Strong foundation in cloud technologies and DevOps pipelines using \textbf{AWS}, \textbf{Docker}, and \textbf{Terraform}. Passionate about clean architecture, code quality, and performance optimization.

% ----- Experience -----
\section*{Experience}
\begin{itemize}[leftmargin=*]

  \resumeSubheading{Health Espresso}{Remote}{Cloud Engineer Co-op}{May 2025 -- Aug. 2025}
  \begin{itemize}
    \resumeItem{Developed over 40 \textbf{Lambda} functions using \textbf{Python} and \textbf{Node.js} for scalable multi-region deployment.}
    \resumeItem{Migrated ZIP-based Lambdas to \textbf{container images}, enabling \textbf{GitHub-integrated CI/CD} and reducing deployment time by 95\%.}
    \resumeItem{Developed modular \textbf{Terraform} templates and integrated \textbf{AWS CodePipeline} for automated provisioning.}
    \resumeItem{Refactored \textbf{IAM policies} to enforce least privilege and automated alias creation via \textbf{Bash scripts}.}
    \resumeItem{Used \textbf{AWS Secrets Manager} and \textbf{Parameter Store} to centralize secure configuration management.}
    \resumeItem{Monitored and troubleshot services using \textbf{CloudWatch Logs} and \textbf{AWS X-Ray}.}
    \resumeItem{Collaborated with developers and QA to deliver stable releases through version-controlled pipelines.}
  \end{itemize}

  \resumeSubheading{Samartha International InfoSolutions}{Kathmandu, Nepal}{Full Stack Developer}{Jun. 2020 -- Aug. 2023}
  \begin{itemize}
    \resumeItem{Delivered production-grade web applications using \textbf{React}, \textbf{ASP.NET Core}, and \textbf{PostgreSQL}.}
    \resumeItem{Designed and implemented REST APIs, authentication systems, and reusable UI components.}
    \resumeItem{Built CI/CD pipelines and Dockerized workloads for consistent and reproducible deployments.}
    \resumeItem{Maintained on-prem \textbf{Kubernetes} clusters (30-node \textbf{vSphere} setup) and containerized workloads.}
  \end{itemize}

\end{itemize}

% ----- Projects -----
\section*{Projects}
\begin{itemize}[leftmargin=*]
  \resumeProjectHeading{PharmaKart (\href{https://github.com/pharmakart/pharmakart-web}{GitHub})}{Jan. 2025 -- Mar. 2025}
  \begin{itemize}
    \resumeItem{Designed and implemented microservices architecture using \textbf{Golang} and \textbf{gRPC} for inter-service communication.}
    \resumeItem{Built scalable APIs with \textbf{clean architecture}, \textbf{JWT authentication}, and \textbf{RBAC roles}.}
    \resumeItem{Optimized performance using \textbf{Redis caching} for product listings, authentication tokens, and order lookups.}
    \resumeItem{Implemented a reminder system using AWS \textbf{Lambda}, \textbf{SNS}, and \textbf{SQS} for asynchronous notifications.}
    \resumeItem{Integrated \textbf{Stripe} for secure payments, refunds, and webhook-based validations.}
    \resumeItem{Deployed microservices to \textbf{EKS} with \textbf{Terraform}, maintaining 99.9\% uptime and seamless CI/CD via \textbf{GitHub Actions}.}
    \resumeItem{Built a responsive frontend using \textbf{Next.js}, \textbf{ShadCN}, and \textbf{Tailwind CSS}.}
\end{itemize}
\end{itemize}

% ----- Education -----
\section*{Education \\ \& Certification}
\begin{itemize}[leftmargin=*]
  \resumeSubheading{Durham College}{Oshawa, ON}{Postgraduate Certificate in Cybersecurity \& Cloud Computing}{Sep. 2023 -- Apr. 2025}
  \begin{itemize}
    \resumeItem{Focused on \textbf{Cloud Security}, \textbf{DevSecOps}, and \textbf{Infrastructure as Code} using \textbf{AWS}, \textbf{Azure}, and \textbf{GCP}.}
    \resumeItem{Gained hands-on experience with \textbf{Kubernetes}, \textbf{Terraform}, \textbf{GitHub Actions}, and \textbf{Jenkins}.}
    \resumeItem{GPA: 4.75 / 5.0}
  \end{itemize}

  \resumeSubheading{Leeds Beckett University}{Leeds, UK}{BSc (Hons) Computing}{Feb. 2019 -- Jul. 2022}
  \begin{itemize}
    \resumeItem{Studied \textbf{SDLC}, \textbf{Web Development}, \textbf{Database Design}, and \textbf{Programming} (Java, C\#, Python).}
    \resumeItem{GPA: 3.8 / 4.0}
  \end{itemize}

  \resumeSubheading{HashiCorp Certified Terraform Associate}{--}{Credential ID: \href{https://www.credly.com/badges/3fc692e0-6068-4337-a077-59e033d1a9d4/public_url}{3fc692e0-6068-4337-a077-59e033d1a9d4}}{Apr. 2025}
\end{itemize}

\end{document}