%-------------------------
% Resume in Latex
% Author : Ashutosh Sharma
% Based off of: https://github.com/jakegut/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
\usepackage{CormorantGaramond}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\setlength{\footskip}{4.08003pt}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-5pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Ashutosh Sharma} \\ \vspace{1pt}
    {Oshawa, ON, Canada} $|$
    \small +1 647-226-0267 $|$ \href{mailto:asrma.sharma@gmail.com}{\underline{asrma.sharma@gmail.com}} $|$ 
    \href{https://linkedin.com/in/asrma7}{\underline{linkedin.com/in/asrma7}} $|$
    \href{https://ashutoshportfolio.site}{\underline{ashutoshportfolio.site}}
\end{center}

%-----------SUMMARY-----------
% \section{Summary}
%   \resumeSubHeadingListStart
%     \item{
%       Cloud \& DevOps Engineer with 3+ years of experience building scalable web applications and managing cloud infrastructure. Skilled in AWS, Kubernetes, and Terraform for infrastructure automation. Experienced with Golang, ASP.NET Core, and React; 7+ years of Linux experience and a Neovim power user. Passionate about developer productivity and building tools that solve real customer problems.
%     }
%   \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Durham College}{Oshawa, ON}
      {Post Graduate Certificate in Cybersecurity \& Cloud Computing}{Sep. 2023 -- Apr. 2025}
      \resumeItemListStart
        \resumeItem{Secure Software Development, Cloud Security, Network Security, Ethical Hacking, Splunk Fundamentals}
        \resumeItem{AWS, Azure, GCP, Kubernetes, Terraform, Jenkins, CodePipeline, GitHub Actions, CI/CD, DevSecOps}
        \resumeItem{\textbf{GPA}: 4.75 / 5.0}
      \resumeItemListEnd

    \resumeSubheading
      {Leeds Beckett University}{Leeds, UK}
      {Bachelor of Science Honours Computing}{Feb. 2019 -- July 2022}
        \resumeItemListStart
            \resumeItem{Software Development, Web Development, Database Management, SDLC, Networking}
            \resumeItem{Java, Python, C\#, JavaScript, HTML, CSS, PHP, ASP.NET, React, Node.js, Express, MongoDB, PostgreSQL}
            \resumeItem{\textbf{GPA}: 3.8 / 4.0}
        \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]

    \small{\item{
        {\textbf{Cloud Platforms}: AWS (EC2, S3, Lambda, ECS, EKS, CloudFormation), Azure, GCP}\\
        {\textbf{DevOps \& IaC}: Docker, Kubernetes, Terraform, Pulumi, Jenkins, GitHub Actions, AWS CodePipeline, Google CloudBuild, Azure DevOps}\\
        {\textbf{Languages}: Golang, TypeScript, JavaScript, Python, C\#, SQL, Bash, AWK, sed}\\
        {\textbf{Frameworks}: React, Next.js, ASP.NET Core, gRPC, Flask, Django (basic)}\\
        {\textbf{Web Technologies}: HTTP/HTTPS, XML, JSON}\\
        {\textbf{Databases}: PostgreSQL, MongoDB, MS SQL, DynamoDB}\\
        {\textbf{Monitoring \& Security}: Prometheus, Grafana, SonarQube, AWS CloudTrail}\\
        {\textbf{Operating Systems}: Linux (Arch, Ubuntu), Windows}\\
        {\textbf{Tools}: Git, Neovim, Shell Scripting, Jira, Internal Tools Development}\\
        {\textbf{Certifications}: HashiCorp Terraform Associate (\href{https://www.credly.com/badges/3fc692e0-6068-4337-a077-59e033d1a9d4/public_url}{\underline{Verified Badge}}), CREATIO Developer (2022)}
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Cloud Engineer Co-op}{May 2025 -- Aug. 2025}
      {Health Espresso (Remote)}{}
      \resumeItemListStart
        \resumeItem{Developed and deployed containerized \textbf{AWS Lambda} functions using \textbf{Docker}, improving maintainability and reducing deployment time by over \textbf{40\%}.}
        \resumeItem{Engineered a Terraform-based CI/CD pipeline with \textbf{AWS CodePipeline} and \textbf{CodeBuild}, enabling seamless promotion of new functions to dev and prod environments.}
        \resumeItem{Wrote robust \textbf{Bash} automation scripts to dynamically generate alias, permissions, and configuration templates for multi-region support.}
        \resumeItem{Optimized \textbf{Terraform} modules, reducing resource duplication and improving reusability across deployments.}
        \resumeItem{Collaborated on technical documentation and cloud service mapping with other co-op students; contributed to over \textbf{10} service diagrams and process documents reviewed by senior engineers.}
      \resumeItemListEnd


    \resumeSubheading
      {Full Stack Developer}{June 2020 -- Aug. 2023}
      {Samartha International InfoSolutions}{Kathmandu, Nepal}
      \resumeItemListStart
        \resumeItem{Spearheaded the development of an E-commerce platform using React, ASP.NET Core, and PostgreSQL.}
        \resumeItem{Leveraged AWS services and CI/CD pipelines to reduce deployment time by 50\%.}
        \resumeItem{Architected CRM \& BPM solutions using ASP.NET and MS SQL to streamline business workflows.}
        \resumeItem{Deployed containerized workloads with Docker \& Kubernetes, optimizing scalability and reducing infrastructure cost by 30\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{PharmaKart} (\href{https://github.com/pharmakart/pharmakart-web}{\underline{Link}}) $|$ \emph{Golang, gRPC, Kubernetes, Terraform, AWS, GitHub Actions, PostgreSQL}}{Jan. 2025 -- Mar. 2025}
          \resumeItemListStart
          \resumeItem{Designed and deployed microservices using \textbf{Golang} and \textbf{gRPC} with JSON-based APIs.}
          \resumeItem{Provisioned AWS infrastructure using \textbf{Terraform} and orchestrated services via \textbf{Kubernetes}.}
          \resumeItem{Set up zero-downtime CI/CD pipelines using \textbf{GitHub Actions} and \textbf{AWS CodePipeline}.}
          \resumeItem{Built and deployed internal admin tooling to manage users, prescriptions, and orders—accelerating support workflows.}
          \resumeItem{Achieved \textbf{99.9\% uptime} using fault-tolerant architecture and proactive Kubernetes resource tuning.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
